Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-19 supplementary_material.tex
add comparison with M15 in SOM

>>>>

\subsection{More Comparisons with GLAD-M15}

In addition to section~7.1, we provide more detailed comparisons with GLAD-M15. Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subudction} shows comparisons n the subduction areas. In both comparison figures, GLAD-M25 shows significant enhancement and emerging features compared to GLAD-M15.

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15($V_\textrm{sv}$, left column) and GLAD-M25($V_\textrm{sv}$; right column).
  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
  }}
  \label{fig:m15_hotspot}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.pdf}
  \caption{\small{ Vertical cross sections for various subduction regions, same as Fig.~\ref{fig:m15_hotspot}.
  (a) Cocos; (b) India; (c) Sumatra; (d) Fiji-Tonga; (e) Farallon; (f) Scotia. }}
  \label{fig:m15_subduction}
\end{figure}
